Single-cell virus sequencing of influenza infections that trigger innate immunity

### 2018-12-24 paper/paper.tex
merged supporting figures for Fig 1 to reduce amount of supp material

% Added by Jesse Bloom for figures
\renewcommand{\floatpagefraction}{.9}
\setcounter{topnumber}{8}
\setcounter{bottomnumber}{8}
\setcounter{totalnumber}{8}

@@

%%% start IFNrare figure %%%
\begin{figure}
\centerline{
{\bf \Large A}\includegraphics[width=0.34\textwidth,valign=t]{figures/IFN_stochastic/IFN_reporter/IFN_reporter.pdf}
\hspace{0.02\textwidth}
{\bf \Large B} \includegraphics[width=0.22\textwidth,valign=t]{figures/IFN_stochastic/Flow/ifn_percent.pdf}
}
\caption{
{\bf Reporter cells to identify and enrich infections that activate IFN expression.}
{\bf (A)} The reporter consists of an IFN promoter that drives expression of a cell-surface protein amenable to MACS and a fluorescent protein.
We created reporters with type I and type III IFN promoters (\SUPPFILE{plasmids}).
In A549 cells, the reporters were efficiently activated by an IFN-inducing strain of Sendai virus (\SUPPFIG{reportervalidation}A).
{\bf (B)}
Frequency of IFN induction upon infection with the influenza virus stock used in the single-cell studies in this paper, as quantified using the type III IFN reporter (see \SUPPFIG{IFNrare_flow} for full flow cytometry data).
The plot also shows uninfected cells, and cells infected with saturating amounts of Sendai virus.
The limit of detection of 0.05\% is indicated with a dashed line, and numbers show the median of three measurements.
}
\label{fig:IFNrare}
\end{figure}
%%% end IFNrare figure %%%

@@

\begin{suppfig}
\begin{minipage}[t]{0.52\textwidth}
{\bf \Large A}

\includegraphics[width=0.9\textwidth, valign=t]{figures/IFN_stochastic/IFN_reporter/Sendai_validation.pdf}
\end{minipage}
\begin{minipage}[t]{0.48\textwidth}
{\bf \Large B}

\includegraphics[width=0.7\textwidth, valign=t]{figures/IFN_stochastic/IFN_reporter/IFNbeta_IFN_lambda_correlated.pdf}

@@

\caption{
{\bf Validation of reporter cell lines (\FIG{IFNrare}A) to identify IFN+ cells.}
{\bf (A)}
To validate the IFN reporter cell lines, they were infected at high MOI with the Cantell strain of Sendai virus, which strongly activates IFN expression~\citep{strahle2006sendai}.
The name of each of reporter cell line is indicated at the top of each row of plots.
At 13 hours post-infection, activation of the IFN reporter was then monitored by flow cytometry using the marker indicated at the bottom of each plot (either a fluorescent protein or antibody staining for the cell-surface LNGFR$\Delta$C using a PE-conjugated anti-LNGFR antibody from Miltenyi Biotec).
Sendai infection efficiently activated the IFN reporter in all cases, with the strongest signal from the IFN-$\lambda$ reporter driving ZsGreen.
{\bf (B)}
The type I and type III IFN reporters are highly correlated in their activation.
An A549 cell line was generated by transduction with both the IFN-$\beta$ and IFN-$\lambda$ reporters driving expression of mCherry and ZsGreen, respectively.
The cells were then infected with two different stocks of ``wild-type'' WSN influenza, or stocks with a deletion in PB1 or stop codons in NS1 (described later in the paper).
After 13 hours, cells were analyzed by flow cytometry.
Cells positive for either fluorescent reporter were further analyzed.
As shown in the FACS plots, expression of the \textit{IFNB1} and \textit{IFNL1} reporters is highly correlated in all cases.
}
\label{suppfig:reportervalidation}
\end{suppfig}

\begin{suppfig}
\includegraphics[width=0.9\textwidth]{figures/IFN_stochastic/Flow/flow_plot.pdf}
\caption{
{\bf Flow cytometry data for \FIG{IFNrare}B.}
The A549 cells with the \textit{IFNL1} reporter driving LNGFR$\Delta$C-ZsGreen were not infected, infected with saturating amounts of the Cantell strain of Sendai virus~\citep{strahle2006sendai}, or infected the same stock of influenza virus used in the single-cell experiment at a target MOI of 0.3.
After 13 hours, the cells were stained for expression of HA protein and analyzed by FACS for HA and expression of the ZsGreen driven by the \textit{IFNL1} reporter.
Each condition was done in triplicate.
The contour plots show the density of all cells, and all IFN+ cells are also indicated by orange dots.
Cells were classified as HA+ or IFN+ based on gates set to put 0.05\% of the uninfected cells in these populations.
For the influenza-infected cells, the percentage IFN+ was calculated only among the HA+ cells (since these are the ones that are infected).
For the uninfected and Sendai-virus infected, the percentage IFN+ was calculated among all cells, since these cells do not express HA.
}
\label{suppfig:IFNrare_flow}
\end{suppfig}

>>>>

% Added by Jesse Bloom for figures
\renewcommand{\floatpagefraction}{0.99}
\renewcommand{\textfraction}{0.01}
\setcounter{topnumber}{8}
\setcounter{bottomnumber}{8}
\setcounter{totalnumber}{8}

@@

%%% start IFNrare figure %%%
\begin{figure}
\centerline{
{\bf \Large A}\includegraphics[width=0.34\textwidth,valign=t]{figures/IFN_stochastic/IFN_reporter/IFN_reporter.pdf}
\hspace{0.02\textwidth}
{\bf \Large B} \includegraphics[width=0.22\textwidth,valign=t]{figures/IFN_stochastic/Flow/ifn_percent.pdf}
}
\caption{
{\bf Reporter cells to identify and enrich infections that activate IFN expression.}
{\bf (A)} The reporter consists of an IFN promoter that drives expression of a cell-surface protein amenable to MACS and a fluorescent protein.
We created reporters with type I and type III IFN promoters (\SUPPFILE{plasmids}).
In A549 cells, the reporters were efficiently activated by an IFN-inducing strain of Sendai virus (\SUPPFIG{reportervalidation}A).
{\bf (B)}
Frequency of IFN induction upon infection with the influenza virus stock used in the single-cell studies in this paper, as quantified using the type III IFN reporter (see \SUPPFIG{reportervalidation}C for full data).
The plot also shows uninfected cells, and cells infected with saturating amounts of Sendai virus.
The limit of detection of 0.05\% is indicated with a dashed line, and numbers show the median of three measurements.
}
\label{fig:IFNrare}
\end{figure}
%%% end IFNrare figure %%%

@@

\begin{suppfig}
\begin{minipage}[t]{0.46\textwidth}
{\bf \Large A}
\includegraphics[width=0.9\textwidth, valign=t]{figures/IFN_stochastic/IFN_reporter/Sendai_validation.pdf}
\end{minipage}
\begin{minipage}[t]{0.55\textwidth}
{\bf \Large B}
\includegraphics[width=0.57\textwidth, valign=t]{figures/IFN_stochastic/IFN_reporter/IFNbeta_IFN_lambda_correlated.pdf}
\vspace{0.1in}

{\bf \Large C}
\includegraphics[width=0.9\textwidth, valign=t]{figures/IFN_stochastic/Flow/flow_plot.pdf}

@@

\caption{
{\bf Validation of IFN reporter, related to \FIG{IFNrare}.}
{\bf (A)}
IFN reporter cell lines were infected at high MOI with the Cantell strain of Sendai virus~\citep{strahle2006sendai}.
The name of the reporter is indicated above the plots.
At 13 hours post-infection, activation of the reporter was monitored by flow cytometry using the marker indicated below each plot (a fluorescent protein or antibody staining for the LNGFR$\Delta$C using PE-conjugated anti-LNGFR antibody from Miltenyi Biotec).
Sendai infection efficiently activated the IFN reporter in all cases.
{\bf (B)}
The type I and type III IFN reporters are highly correlated in their activation.
An A549 cell line was generated by transduction with both IFN-$\beta$ and IFN-$\lambda$ reporters driving mCherry and ZsGreen, respectively.
The cells were infected with two different stocks of WSN influenza, or stocks with a deletion in PB1 or stop codons in NS1.
After 13 hours, cells were analyzed by flow cytometry.
Cells positive for either reporter were further analyzed.
As shown in the FACS plots, expression of the \textit{IFNB1} and \textit{IFNL1} reporters is highly correlated.
{\bf (C)}
Flow cytometry data for \FIG{IFNrare}B.
A549 cells with the \textit{IFNL1} reporter driving LNGFR$\Delta$C-ZsGreen were not infected, infected with saturating amounts of the Cantell strain of Sendai virus, or infected at a target MOI of 0.3 with the stock of influenza virus used in the single-cell experiment.
At 13 hours, cells were analyzed by FACS for HA and ZsGreen expression.
Each condition was done in triplicate.
Contour plots show density of all cells, and IFN+ cells are also indicated by orange dots.
Cells were classified as HA+ or IFN+ based on gates set to put 0.05\% of the uninfected cells in these populations.
For influenza-infected cells, the percentage IFN+ was calculated only among HA+ cells (since these are the ones that are infected).
For uninfected and Sendai-infected cells, the percentage IFN+ was calculated among all cells, since the cells do not express HA.
}
\label{suppfig:reportervalidation}
\end{suppfig}
